|

### 2021-06-23 paper.Rmd
Title page update.

---
title: |
  |
  | 
  | \vspace{1cm}Writing a reproducible paper
  | in R Markdown*^[*Corresponding address: mail@paulcbauer.eu. Acknowledgments: I am grateful to all those generous people that invest their time into open-source software.]\vspace{0.5cm}
  |
author: |
  | Paul C. Bauer
  | Mannheim Centre for European Social Research
date: |
  |       
  | First version: December 14, 2018
  | This version: `r gsub("^0", "", format(Sys.time(), "%B %d, %Y"))`
  |
  | Feedback? 
  | mail@paulcbauer.eu
  |
linestretch: 1.2
colorlinks: true
abstract: \noindent\setstretch{1}The present paper provides a template for a reproducible scientific paper written in R Markdown. Below I outline some of the "tricks"/code (e.g., referencing tables, sections etc.) I had to figure out to produce this document. The underlying files which produce this document can be downloaded [here](https://drive.google.com/drive/folders/1zJP3cNPrHN-gj0rcmbHQgg-XA0hqDXdd?usp=sharing). I think I got pretty far but there is always room for improvement and more automatization, in parallel to the incredible developments in R and Rstudio (bookdown etc.). I intend to update this file when I discover more convenient code (you can follow any updates through the corresponding [github repo](https://github.com/paulcbauer/Writing_a_reproducable_paper_in_rmarkdown/)).\vspace{.8cm}
bibliography: references.bib
csl: american-sociological-association.csl
output:
  bookdown::pdf_document2:
    toc: no
    keep_tex: true
mainfont: Times New Roman
sansfont: Times New Roman
fontsize: 12pt
link-citations: true
documentclass: article
geometry: margin=1in
always_allow_html: yes
---

@@

* Keep all files of your project (that matter for producing the PDF) in one folder without subfolders. You can zip and directly upload that folder to the [Harvard dataverse](https://dataverse.harvard.edu/).
* Make sure that filenames have a logic to them.
    + Main file with text/code: "paper.rmd", "report.rmd" 
    + Data files: "data_xxxxxx.*"
    + Image files: "fig_xxxxxx.*"
    + Tables files: "table_xxxx.*"
    + etc.
    + Ideally, your filenames will correspond to the names in the paper. For instance, Figure 1 in the paper may have a corresponding file called `fig_1_xxxxx.pdf`.
* Use the document outline in R studio (Ctrl + Shift + O) when you work with R Markdown.
* Name rchunks according to what they do or produce:
    + "`fig-...`" for chunks producing figures
    + "`table-...`" for chunks producing tables
    + "`model-...`" for chunks producing model estimates
    + "`import-...`" for chunks importing data
    + "`recoding-...`" for chunks in which data is recoded
* Use "really" informative variable names:
    + Q: What do you think does the variable *trstep* measure? It actually measures trust in the European parliament. 
        + How could we call this variable instead? Yes, `trust.european.parliament` which is longer but will probably be understood by another researcher. 
    + If your setup is truly reproducible you will probably re-use the variable names that you generate as variable names in the tables you produce. Hence, there is an incentive to use good names.
* Use unique identifiers in the final document:
    + e.g., name the models you estimate "M1", "M2" etc.
    + These unique names should also appear in the published paper.
    + Think of someone who wants to produce Figure 1/Model 1 in your paper but doesn't find it in your code...

>>>>

---
title: |
  |
  | 
  | \vspace{1cm}Writing a reproducible paper
  | in R Markdown*^[*Corresponding address: mail@paulcbauer.eu. Acknowledgments: I am grateful to all those generous people that invest their time into open-source software.]\vspace{0.5cm}
  |
author: |
  | Paul C. Bauer
  | Mannheim Centre for European Social Research
date: |
  |       
  | First version: December 14, 2018
  | This version: `r gsub("^0", "", format(Sys.time(), "%B %d, %Y"))`
  |
  | Feedback? Errors?
  | mail@paulcbauer.eu
  | [Github repository](https://github.com/paulcbauer/Writing_a_reproducable_paper_in_rmarkdown/)
  |
  |
  | Tired of Latex?
  | Try [Pagedown](https://github.com/rstudio/pagedown) with our [new template](https://osf.io/k8jhx/)! :-)
linestretch: 1.2
colorlinks: true
abstract: \noindent\setstretch{1}The present paper provides a template for a reproducible scientific paper written in R Markdown. Below I outline some of the "tricks"/code (e.g., referencing tables, sections etc.) I had to figure out to produce this document. The underlying files which produce this document can be downloaded [here](https://drive.google.com/drive/folders/1zJP3cNPrHN-gj0rcmbHQgg-XA0hqDXdd?usp=sharing). I think I got pretty far but there is always room for improvement and more automatization, in parallel to the incredible developments in R and Rstudio (bookdown etc.). I intend to update this file when I discover more convenient code (you can follow any updates through the corresponding [github repo](https://github.com/paulcbauer/Writing_a_reproducable_paper_in_rmarkdown/)).\vspace{.8cm}
bibliography: references.bib
csl: american-sociological-association.csl
output:
  bookdown::pdf_document2:
    toc: no
    keep_tex: true
mainfont: Times New Roman
sansfont: Times New Roman
fontsize: 12pt
link-citations: true
documentclass: article
geometry: margin=1in
always_allow_html: yes
---

@@

* Keep all files of your project (that matter for producing the PDF) in one folder without subfolders. You can zip and directly upload that folder to the [Harvard dataverse](https://dataverse.harvard.edu/).
* Make sure that filenames have a logic to them.
    + Main file with text/code: "paper.rmd", "report.rmd" 
    + Data files: "data_xxxxxx.*"
    + Image files: "fig_xxxxxx.*"
    + Tables files: "table_xxxx.*"
    + etc.
    + Ideally, your filenames will correspond to the names in the paper. For instance, Figure 1 in the paper may have a corresponding file called `fig_1_xxxxx.pdf`.
* Use the document outline in R studio (Ctrl + Shift + O) when you work with R Markdown.
* Name rchunks according to what they do or produce:
    + "`fig-...`" for chunks producing figures
    + "`table-...`" for chunks producing tables
    + "`model-...`" for chunks producing model estimates
    + "`import-...`" for chunks importing data
    + "`recoding-...`" for chunks in which data is recoded
* Ideally give chunks the labels of the figures/tables in the final publication, e.g., "`fig-1`" is the name of the chunk that produces Figure 1 in the final paper.
* Use "really" informative variable names:
    + Q: What do you think does the variable *trstep* measure? It actually measures trust in the European parliament. 
        + How could we call this variable instead? Yes, `trust.european.parliament` which is longer but will probably be understood by another researcher. 
    + If your setup is truly reproducible you will probably re-use the variable names that you generate as variable names in the tables you produce. Hence, there is an incentive to use good names.
* Use unique identifiers in the final document:
    + e.g., name the models you estimate "M1", "M2" etc.
    + These unique names should also appear in the published paper.
    + Think of someone who wants to produce Figure 1/Model 1 in your paper but doesn't find it in your code...

### 2021-06-23 paper.tex
Title page update.

\title{\vspace{1cm}Writing a reproducible paper\\
in R Markdown*\footnote{*Corresponding address: \href{mailto:mail@paulcbauer.eu}{\nolinkurl{mail@paulcbauer.eu}}. Acknowledgments: I am grateful to all those generous people that invest their time into open-source software.}\vspace{0.5cm}\\}
\author{Paul C. Bauer\\
Mannheim Centre for European Social Research}
\date{First version: December 14, 2018\\
This version: July 08, 2020\\
~\\
Feedback? Errors?\\
\href{mailto:mail@paulcbauer.eu}{\nolinkurl{mail@paulcbauer.eu}}\\
\href{https://github.com/paulcbauer/Writing_a_reproducable_paper_in_rmarkdown/}{Github repository}}

@@

\caption{\label{tab:tab3}Table with kable() and kablestyling()}
\centering
\resizebox{\linewidth}{!}{
\fontsize{10}{12}\selectfont
\begin{tabu} to \linewidth {>{\raggedright}X>{\raggedleft}X>{\raggedleft}X}
\toprule
  & speed & dist\\
\midrule
\rowcolor{gray!6}  1 & 4 & 2\\
2 & 4 & 10\\
\rowcolor{gray!6}  3 & 7 & 4\\
4 & 7 & 22\\
\rowcolor{gray!6}  5 & 8 & 16\\
\addlinespace
6 & 9 & 10\\
\rowcolor{gray!6}  7 & 10 & 18\\
8 & 10 & 26\\
\rowcolor{gray!6}  9 & 10 & 34\\
10 & 11 & 17\\
\bottomrule
\end{tabu}}
\end{table}

@@

  \begin{itemize}
  \tightlist
  \item
    ``\texttt{fig-...}'' for chunks producing figures
  \item
    ``\texttt{table-...}'' for chunks producing tables
  \item
    ``\texttt{model-...}'' for chunks producing model estimates
  \item
    ``\texttt{import-...}'' for chunks importing data
  \item
    ``\texttt{recoding-...}'' for chunks in which data is recoded
  \end{itemize}
\item
  Use ``really'' informative variable names:

@@

\begin{verbatim}
## R version 4.0.0 (2020-04-24)
## Platform: x86_64-w64-mingw32/x64 (64-bit)
## Running under: Windows 10 x64 (build 17763)
## 
## Matrix products: default
## 
## attached base packages:
## [1] stats     graphics  grDevices utils     datasets  methods   base     
## 
## other attached packages:
## [1] ggplot2_3.3.0    kableExtra_1.1.0 knitr_1.29       stargazer_5.2.2 
## 
## loaded via a namespace (and not attached):
##  [1] Rcpp_1.0.4.6      pillar_1.4.4      compiler_4.0.0    tools_4.0.0      
##  [5] digest_0.6.25     evaluate_0.14     lifecycle_0.2.0   tibble_3.0.1     
##  [9] gtable_0.3.0      viridisLite_0.3.0 pkgconfig_2.0.3   rlang_0.4.6      
## [13] rstudioapi_0.11   yaml_2.2.1        xfun_0.15         withr_2.2.0      
## [17] stringr_1.4.0     httr_1.4.1        dplyr_1.0.0       xml2_1.3.2       
## [21] generics_0.0.2    vctrs_0.3.1       hms_0.5.3         tidyselect_1.1.0 
## [25] webshot_0.5.2     grid_4.0.0        glue_1.4.1        R6_2.4.1         
## [29] rmarkdown_2.3     bookdown_0.19     farver_2.0.3      purrr_0.3.4      
## [33] readr_1.3.1       magrittr_1.5      scales_1.1.1      ellipsis_0.3.1   
## [37] htmltools_0.5.0   rvest_0.3.5       colorspace_1.4-1  labeling_0.3     
## [41] stringi_1.4.6     munsell_0.5.0     crayon_1.3.4
\end{verbatim}

>>>>

\title{\vspace{1cm}Writing a reproducible paper\\
in R Markdown*\footnote{*Corresponding address: \href{mailto:mail@paulcbauer.eu}{\nolinkurl{mail@paulcbauer.eu}}. Acknowledgments: I am grateful to all those generous people that invest their time into open-source software.}\vspace{0.5cm}\\}
\author{Paul C. Bauer\\
Mannheim Centre for European Social Research}
\date{First version: December 14, 2018\\
This version: June 23, 2021\\
~\\
Feedback? Errors?\\
\href{mailto:mail@paulcbauer.eu}{\nolinkurl{mail@paulcbauer.eu}}\\
\href{https://github.com/paulcbauer/Writing_a_reproducable_paper_in_rmarkdown/}{Github repository}\\
~\\
~\\
Tired of Latex?\\
Try \href{https://github.com/rstudio/pagedown}{Pagedown} with our \href{https://osf.io/k8jhx/}{new template}! :-)}

@@

\caption{\label{tab:tab3}Table with kable() and kablestyling()}
\centering
\resizebox{\linewidth}{!}{
\fontsize{10}{12}\selectfont
\begin{tabu} to \linewidth {>{\raggedright}X>{\raggedleft}X>{\raggedleft}X}
\toprule
  & speed & dist\\
\midrule
\cellcolor{gray!6}{1} & \cellcolor{gray!6}{4} & \cellcolor{gray!6}{2}\\
2 & 4 & 10\\
\cellcolor{gray!6}{3} & \cellcolor{gray!6}{7} & \cellcolor{gray!6}{4}\\
4 & 7 & 22\\
\cellcolor{gray!6}{5} & \cellcolor{gray!6}{8} & \cellcolor{gray!6}{16}\\
\addlinespace
6 & 9 & 10\\
\cellcolor{gray!6}{7} & \cellcolor{gray!6}{10} & \cellcolor{gray!6}{18}\\
8 & 10 & 26\\
\cellcolor{gray!6}{9} & \cellcolor{gray!6}{10} & \cellcolor{gray!6}{34}\\
10 & 11 & 17\\
\bottomrule
\end{tabu}}
\end{table}

@@

  \begin{itemize}
  \tightlist
  \item
    ``\texttt{fig-...}'' for chunks producing figures
  \item
    ``\texttt{table-...}'' for chunks producing tables
  \item
    ``\texttt{model-...}'' for chunks producing model estimates
  \item
    ``\texttt{import-...}'' for chunks importing data
  \item
    ``\texttt{recoding-...}'' for chunks in which data is recoded
  \end{itemize}
\item
  Ideally give chunks the labels of the figures/tables in the final publication, e.g., ``\texttt{fig-1}'' is the name of the chunk that produces Figure 1 in the final paper.
\item
  Use ``really'' informative variable names:

@@

\begin{verbatim}
## R version 4.1.0 (2021-05-18)
## Platform: x86_64-w64-mingw32/x64 (64-bit)
## Running under: Windows 10 x64 (build 17763)
## 
## Matrix products: default
## 
## attached base packages:
## [1] stats     graphics  grDevices utils     datasets  methods   base     
## 
## other attached packages:
## [1] ggplot2_3.3.4    kableExtra_1.3.4 knitr_1.33       stargazer_5.2.2 
## 
## loaded via a namespace (and not attached):
##  [1] compiler_4.1.0    pillar_1.6.1      tools_4.1.0       digest_0.6.27    
##  [5] evaluate_0.14     lifecycle_1.0.0   tibble_3.1.2      gtable_0.3.0     
##  [9] viridisLite_0.4.0 pkgconfig_2.0.3   rlang_0.4.11      DBI_1.1.1        
## [13] rstudioapi_0.13   yaml_2.2.1        xfun_0.24         withr_2.4.2      
## [17] dplyr_1.0.6       httr_1.4.2        stringr_1.4.0     xml2_1.3.2       
## [21] generics_0.1.0    vctrs_0.3.8       systemfonts_1.0.2 tidyselect_1.1.1 
## [25] webshot_0.5.2     grid_4.1.0        svglite_2.0.0     glue_1.4.2       
## [29] R6_2.5.0          fansi_0.5.0       rmarkdown_2.9     bookdown_0.22    
## [33] farver_2.1.0      purrr_0.3.4       magrittr_2.0.1    scales_1.1.1     
## [37] htmltools_0.5.1.1 ellipsis_0.3.2    assertthat_0.2.1  rvest_1.0.0      
## [41] colorspace_2.0-1  labeling_0.4.2    utf8_1.2.1        stringi_1.6.1    
## [45] munsell_0.5.0     crayon_1.4.1
\end{verbatim}
